Stochastic Variance Reduced Policy Gradient

### 2018-02-02 svrpg.tex
correzioni

We have already said that as the number of sub-iterations $m$ increases the variance of the importance weights increases too. Therefore, the SVRPG algorithm fails in its primary aim of stabilizing the gradient estimate.

@@

>>>>

We have already said that as the number of sub-iterations $m$ increases the variance of the importance weights increases too. Therefore, if $m$ is not properly set the SVRPG algorithm fails in its primary aim of stabilizing the gradient estimate.

@@

We introduce a term with importance weights to guarantee proper sampling of trajectories.
This term's variance is subjected to the variance of importance weights. 
There are some methods to reduce this variance.
